### 2013-09-27 manuscripts/dpp-msbayes/dpp-msbayes.tex
Starting to add validation accuracy plots to dpp ms.
Adding more figures to dpp ms.

%:FIGURE-accuracy omega SS GLM
\begin{figure}[hbtp]
    \captionsetup{listformat=figList}
    \centering
    \includegraphics[width=1.0\textwidth]{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-dpp_mc_behavior.pdf}
    \caption{
        Model-choice behavior \ldots
    }
    \label{fig_dpp_dpp_val_mc}
\end{figure}

>>>>

%% Validation accuracy
\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelDPP}
}{figValidationAccuracyDPPDPP}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelUniform}
}{figValidationAccuracyDPPUniform}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelOld}
}{figValidationAccuracyDPPOld}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPP}{\modelUshaped}
}{figValidationAccuracyDPPUshaped}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelDPP}
}{figValidationAccuracyUniformDPP}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelUniform}
}{figValidationAccuracyUniformUniform}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelOld}
}{figValidationAccuracyUniformOld}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelUniform}{\modelUshaped}
}{figValidationAccuracyUniformUshaped}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelDPP}
}{figValidationAccuracyOldDPP}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelUniform}
}{figValidationAccuracyOldUniform}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelOld}
}{figValidationAccuracyOldOld}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelOld}{\modelUshaped}
}{figValidationAccuracyOldUshaped}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelDPP}
}{figValidationAccuracyUshapedDPP}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-uniform_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelUniform}
}{figValidationAccuracyUshapedUniform}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-old_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelOld}
}{figValidationAccuracyUshapedOld}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-u-shaped_accuracy.pdf}{
    \validationAccuracyCaption{\modelUshaped}{\modelUshaped}
}{figValidationAccuracyUshapedUshaped}

%% Validation model choice
\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelDPP}
}{figValidationModelChoiceDPPDPP}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelUniform}
}{figValidationModelChoiceDPPUniform}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelOld}
}{figValidationModelChoiceDPPOld}

\mFigure{../../validation/results/dpp/pymsbayes-results/plots/prior-dpp_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPP}{\modelUshaped}
}{figValidationModelChoiceDPPUshaped}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelDPP}
}{figValidationModelChoiceUniformDPP}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelUniform}
}{figValidationModelChoiceUniformUniform}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelOld}
}{figValidationModelChoiceUniformOld}

\mFigure{../../validation/results/uniform/pymsbayes-results/plots/prior-uniform_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUniform}{\modelUshaped}
}{figValidationModelChoiceUniformUshaped}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelDPP}
}{figValidationModelChoiceOldDPP}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelUniform}
}{figValidationModelChoiceOldUniform}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelOld}
}{figValidationModelChoiceOldOld}

\mFigure{../../validation/results/old/pymsbayes-results/plots/prior-old_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelOld}{\modelUshaped}
}{figValidationModelChoiceOldUshaped}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelDPP}
}{figValidationModelChoiceUshapedDPP}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-uniform_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelUniform}
}{figValidationModelChoiceUshapedUniform}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-old_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelOld}
}{figValidationModelChoiceUshapedOld}

\mFigure{../../validation/results/u-shaped/pymsbayes-results/plots/prior-u-shaped_prior-u-shaped_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelUshaped}{\modelUshaped}
}{figValidationModelChoiceUshapedUshaped}

%% Validation ordered models
\mFigure{../../validation/no-sort/results/pymsbayes-results/plots/prior-dpp_prior-dpp_accuracy.pdf}{
    \validationAccuracyCaption{\modelDPPOrdered}{\modelDPPOrdered}
}{figValidationAccuracyDPPOrderedDPPOrdered}

\mFigure{../../validation/no-sort/results/pymsbayes-results/plots/prior-dpp_prior-dpp_mc_behavior.pdf}{
    \validationModelChoiceCaption{\modelDPPOrdered}{\modelDPPOrdered}
}{figValidationModelChoiceDPPOrderedDPPOrdered}
